Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-12 eswc-2012/phdsymp.tex
sort of a conclusion
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@181 43ef1190-90fd-4dd7-a769-d0121f02b80e
titlerunning
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@182 43ef1190-90fd-4dd7-a769-d0121f02b80e
paste bibliography for submission
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@183 43ef1190-90fd-4dd7-a769-d0121f02b80e

\title{Sharing statistics for SPARQL Federation optimization, with
  emphasis on benchmark quality}
\titlerunning{Sharing statistics and benchmarking for SPARQL federation}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway
\email{kjekje@ifi.uio.no}}

@@

\bibliographystyle{plain-csmin}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}

>>>>

\title{Sharing statistics for SPARQL Federation optimization, with
  emphasis on benchmark quality}
\titlerunning{Sharing statistics and benchmarks for SPARQL federation}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway
\email{kjekje@ifi.uio.no}}

@@

This approach will yield the contributions listed above if completely
successful, but will also advance the state of the art if only
partially successful.

%\bibliographystyle{plain-csmin}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
%\bibliography{selectivity,federation,benchmarks,optimization}

\begin{thebibliography}{1}

\bibitem{springerlink:10.1007/978-3-642-21064-8-1}
C. Buil-Aranda, M. Arenas, and O. Corcho.
\newblock Semantics and optimization of the {SPARQL} 1.1 federation extension.
\newblock In {\em The Semanic Web: Research and Applications}, LNCS\,6644:1-15,
  2011.

\bibitem{Duan:2011:AOC:1989323.1989340}
S. Duan, A. Kementsietsidis, K. Srinivas, and O. Udrea.
\newblock Apples and oranges: a comparison of {RDF} benchmarks and real {RDF}
  datasets.
\newblock In {\em Proc. of the 2011 Int. Conf. on Management of data}, SIGMOD
  '11, pages 145--156, 2011. ACM.

\bibitem{Getoor:2001:SEU:375663.375727}
L. Getoor, B. Taskar, and D. Koller.
\newblock Selectivity estimation using probabilistic models.
\newblock In {\em Proc. of the 2001 ACM SIGMOD Int. Conf. on Management of
  data}, SIGMOD '01, pages 461--472, 2001. ACM.

\bibitem{springerlink:10.1007/978-3-642-17551-0-5}
O. G\"orlitz and S. Staab.
\newblock Federated data management and query optimization for linked open
  data.
\newblock In {\em New Directions in Web Data Management 1}, volume 331 of {\em
  Studies in Computational Intelligence}, pages 109--137. Springer, 2011.

\bibitem{Harth:2010:DSO:1772690.1772733}
A. Harth, K. Hose, M. Karnstedt, A. Polleres, K.-U. Sattler, and J. Umbrich.
\newblock Data summaries for on-demand queries over linked data.
\newblock In {\em Proc. of the 19th Int. Conf. on World wide web}, WWW '10,
  pages 411--420, 2010. ACM.

\bibitem{mxro:Morsey2011DBpedia}
M. Morsey, J. Lehmann, S. Auer, and A.-C.~N. Ngomo.
\newblock {{DBpedia} {SPARQL} Benchmark - Performance Assessment with Real
  Queries on Real Data}.
\newblock In {\em 10th International Semantic Web Conference (ISWC2011)}, 2011.

\bibitem{Schmidt:2011:FBS:2063016.2063054}
M. Schmidt, O. G\"{o}rlitz, P. Haase, G. Ladwig, A. Schwarte, and T. Tran.
\newblock {FedBench}: a benchmark suite for federated semantic data query
  processing.
\newblock In {\em Proc. of the 10th Int. Conf. on The semantic web - Volume
  Part I}, LNCS\,7031:585--600, 2011.

\bibitem{springerlink:10.1007/978-3-642-25073-6-38}
A. Schwarte, P. Haase, K. Hose, R. Schenkel, and M. Schmidt.
\newblock {FedX}: Optimization techniques for federated query processing on
  linked data.
\newblock In {\em The Semantic Web - ISWC 2011}, LNCS\,7031:601-616.

\end{thebibliography}
